Reionization Planck 2018 Notes

### 2020-12-03 results/notes.tex
Updates from Overleaf

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{paper/plots/plot_mj_triangle_t18_r12_t19_t20_vs_pl18_pc_zmax30_pliklite_srollv2_1015_wTauTrajectory_pl15_wTanhML_wGaussEllipse.pdf}
    \caption{Caption}
    \label{fig:plot_triangle_wGauss}
\end{figure}

@@

\begin{figure}

\includegraphics[width=0.4\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run1_f0p28_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.4\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run1_f0p28_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run4_f0p18_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
\includegraphics[width=0.4\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run3_f0p10_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
\label{fig:}
\caption{Top 2x2 panels: Automated getdist smoothing (left column) and hand tuned smoothing (right column) for f = 0.14 and f = 0.28. Bottom 2 panels: f = 0.18 and f = 0.1 for the same hand tuned smoothing settings (slightly aggressive binning).
} 
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0393_tri.png}
%    \caption{$\taulo$ prior imposed at 0.0393, giving a straight cut in the 2D constraint, rather than the rounded zre = 6.1 prior.}
%    \label{fig:my_label}
%\end{figure}
